Setting up Data

### 2020-02-25 src/SetupData.Rmd
small changes

mini.MLH1_datamouse.table <- ddply(MLH1_data, c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(Random.Name),
                        #most recent date
                        oldest = min(date.imaged),
                        newest = max(date.imaged)

)

>>>>

#mini.MLH1_datamouse.table <- ddply(MLH1_data, c("mouse"), summarise,
#                        Nmice = length(unique(mouse)),
#                        Ncells  = length(Random.Name),
#                        #most recent date
#                        oldest = min(date.imaged),
#                        newest = max(date.imaged)
#)
